Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
App. D.2

\subsection{Uncertainty quantification on UCI data sets}
\label{app:uci}
%
In \cref{sec:uci} in the main paper, we showed experiments on 8 UCI data sets \cite{UCI} matching those presented in \cite{immer2021improving}. For direct comparison, we replicate the benchmark as in \cite{immer2021improving}: for each data set, we run the neural network training and the \our prediction pipeline on 10 values of prior precision $\delta$ and 10 seeds matching those used in \cite{immer2021improving}. After completing these 100 runs, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables. The range of $\delta$ used for the hyperparameter search varies depending on data set and the number of inducing points. Below we list the selected $\delta$ ranges:
\begin{itemize}
\item {\sc digits}: The ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
\item {\sc cancer}: For $M > 128$, the ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$. With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
\item {\sc satellite}: For $M < 512$, the tend $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
\item {\sc satellite}: For $M \geq 512$, the ten $\delta$ values are logspaced between $10^{1}$ and $10^2$.  With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
\item Othewise: The ten $\delta$ values are logspaced between $10^{-2}$ and $10^2$, matching \cite{immer2021improving}.
\end{itemize}

@@

All neural network designs and related hyperparameters are set as in \cite{immer2021improving} for a fair comparison, for instance we train the 2-layer MLPs with learning rate $0.001$ for 10,000 epochs, using the full data set instead of batching. In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512\}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results. Our code implementation of the UCI experiments has been built on top of the code provided for \cite{immer2021improving}, using the \our methods provided in the supplementary material.

@@

For the image-based classification experiments,
we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
For the neural network training, we used the same set-up as in \citet{immer2021improving},
training the neural networok using Adam for $500$ epochs using a batch size of $512$.
The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
and we ran each experiment for $5$ seeds.
The MNIST experiments used a prior precision of $\delta=0.0008$
and the FMNIST experiments used a prior precision of $\delta=0.0013$.
The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activtions.
In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
architecture with two fully connected classification layers and Tanh activations.

In contrast to the GP subset implementation in \citet{immer2021improving},
we do not perform scaling of $\delta$ after the neural network has been trained.
Instead, we use the same prior precision that was used during training.
We performeed a grid search over the prior precision for the NN MAP using the validation NLPD.
We then used this prior precision for the GP predictive (NN) with $M=1024$,
GP predictive with $M=1024$, SFR (NN) and SFR.
We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.

>>>>

\subsection{Uncertainty quantification on UCI data sets}
\label{app:uci}
%
In \cref{sec:uci} in the main paper, we showed experiments on 8 UCI data sets \cite{UCI} matching those presented in \cite{immer2021improving}. For direct comparison, we replicate the benchmark as in \cite{immer2021improving}: for each data set, we run the neural network training and the \our prediction pipeline on 10 values of prior precision $\delta$ and 10 seeds matching those used in \cite{immer2021improving}. After completing these 100 runs, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables. The range of $\delta$ used for the hyperparameter search varies depending on data set and the number of inducing points. Below we list the selected $\delta$ ranges:
\begin{itemize}
\item {\sc digits}: The ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching~\cite{immer2021improving}.
\item {\sc cancer}: For $M > 128$, the ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$. With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
\item {\sc satellite}: For $M < 512$, the tend $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching~\cite{immer2021improving}.
\item {\sc satellite}: For $M \geq 512$, the ten $\delta$ values are logspaced between $10^{1}$ and $10^2$.  With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
\item Othewise: The ten $\delta$ values are logspaced between $10^{-2}$ and $10^2$, matching~\cite{immer2021improving}.
\end{itemize}

@@

All neural network designs and related hyperparameters are set as in \cite{immer2021improving} for a fair comparison, for instance we train the 2-layer MLPs with learning rate $0.001$ for 10,000 epochs, using the full data set instead of batching. In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512\}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.

Our code implementation of the UCI experiments has been built on top of the code provided for \cite{immer2021improving}, using the \our method, and is provided in the supplementary material zip file.

@@

In \cref{sec:image} in the main paper, we included experiments on image data sets. For the image-based classification experiments, we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
For the neural network training, we used the same set-up as in \cite{immer2021improving},
training the neural networok using Adam for $500$ epochs using a batch size of $512$.
The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
and we ran each experiment for $5$ seeds.
The MNIST experiments used a prior precision of $\delta=0.0008$
and the FMNIST experiments used a prior precision of $\delta=0.0013$.
The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activtions.
In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
architecture with two fully connected classification layers and tanh activations.

In contrast to the GP subset implementation in \citet{immer2021improving},
we do not perform scaling of $\delta$ after the neural network has been trained.
Instead, we use the same prior precision that was used during training.
We performeed a grid search over the prior precision for the NN MAP using the validation NLPD.
We then used this prior precision for the GP predictive (NN) with $M=1024$,
GP predictive with $M=1024$, \our (NN) and \our.
We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.
